---
title: "Benchmark for ESSD"
author: "EUMETNET verification team"
date: "`r Sys.Date()`"
output: html_document
---

# Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
This is an attempt at automatically installing dependencies.
A better integrated way (e.g. `ESSD-verification` as a package) may be implemented at a later stage.

```{r libraries}
dependencies <- c('dplyr', 'ncdf4', 'ncdf4.helpers', 'tibble', 'tidync', 'ggplot2', 'tidyr', 'SpecsVerification', 'verification', 'zoo', 'rmarkdown', 'knitr')
for (pkg in dependencies) {
  if (!requireNamespace(pkg, quietly = TRUE)) {
    install.packages(pkg)
  }
}

source("read_data.R")
source("verif_functions.R")

```

Before you load the data, please make sure that your path points to the directory downloaded from [https://cloud.meteo.be/s/BzYNiaEYoWX8gnA](`cloud.meteo.be`).

```{r data}
## set the path to your data directory
path <- "data"

obsfile <- list.files(path, "observations.nc", full.names = TRUE)
# exclude ZAMG v1.0 from being assessed due to wrong data format
fcfiles <- setdiff(
  list.files(path, ".nc$", full.names = TRUE), 
  c(obsfile, "1_ESSD-benchmark_ZAMG_EMOS-v1.0.nc")
)

## read observations
obs <- obsfile %>% 
  tidync::tidync("t2m") %>%
  tidync::hyper_tibble(na.rm = FALSE) %>%
  dplyr::mutate(
    time = as.POSIXct("1970-01-01", tz = 'UTC') + 
      as.difftime(time, units = "secs")
  ) %>%
  dplyr::rename(obs = t2m)

## read station metadata
stations <- obsfile %>%
  tidync::tidync("D0") %>% 
  tidync::hyper_tibble(na.rm = FALSE)
```

The observations are read into a data frame with four columns. 
The observed values are stored in the column named `obs`.

```{r obs}
obs
```


The forecasts follow the same format, with the exception that the ensemble or quantile forecast is stored as an matrix column. 
This matrix column contains the 51 realizations (quantiles). 

```{r fcst}
read_file(fcfiles[1])
```
Additional station metadata is extracted from the `*observations.nc` file.
```{r stations}
stations
```

# Scores

Scores are computed by joining the forecast and observation data frames on the common dimensions.
This ensures that the ordering is correct (if correctly specified).

```{r scores}
scores <- lapply(fcfiles, compute_scores, obs = obs) %>%
  dplyr::bind_rows()
```

Aggregates can be computed by using `group_by` and `summarize`.

```{r score_mn}
scores_mn <- scores %>%
  tidyr::drop_na() %>% 
  dplyr::group_by(source, step) %>%
  dplyr::summarize(
    bias = mean(mn - obs),
    mae = mean(abs(mn - obs)), 
    rmse = sqrt(mean((mn - obs)**2)), 
    sd = mean(sd), 
    crps = mean(crps), 
    .groups = "drop"
  ) %>% 
  dplyr::mutate(
    s2e = sd / rmse
  )

scores_map <- scores %>% 
  tidyr::drop_na() %>%
  dplyr::group_by(source, station_id) %>%
  dplyr::summarize(
    bias = mean(mn - obs),
    mn = mean(mn), 
    obs = mean(obs),
    .groups = "drop"
  ) %>%
  left_join(stations, by = "station_id")
```

Some of the mis-specified files may not be sorted as expected, as shown by the correlation of ensemble mean and observed mean at stations.
Datasets with very low correlation are excluded from further analysis. 

```{r check}
map_cor <- scores_map %>% 
  group_by(source) %>%
  summarize(cor = cor(mn, obs))

okish <- map_cor %>%
  dplyr::filter(cor > 0.7) %>%
  dplyr::pull("source")

map_cor
```

# Results

We start with a plot of scores by lead time.

```{r leadtime}
library(ggplot2)

scores_mn %>%
  dplyr::filter(source %in% okish) %>%
  tidyr::pivot_longer(-c(source, step)) %>%
  ggplot(aes(x = step, y = value, col = source)) + 
  geom_line() + 
  facet_wrap(~ name, scales= "free_y", nrow = 3) + 
  theme_light()
```


A map of the bias can be produced as follows.

```{r map}
scores_map %>%
  dplyr::filter(source %in% okish) %>%
  ggplot(aes(x = longitude, y = latitude)) + 
  borders(
    xlim = range(scores_map$longitude), 
    ylim = range(scores_map$latitude)
  ) + 
  geom_point(aes(fill = bias), pch = 21, size = 3) + 
  facet_wrap(~source) + 
  scale_fill_gradient2(low = "darkblue", high = "darkred") + 
  coord_fixed(
    ratio = 1/ cos(50/180*pi),
    xlim = range(scores_map$longitude), 
    ylim = range(scores_map$latitude)
  ) +
  theme_void()
```

Rank histograms are produced as follows.

```{r rank-histogram}
scores %>% 
  tidyr::drop_na() %>% 
  group_by(source, rank) %>%
  count() %>%
  ggplot(aes(x = rank, y = n)) + 
  geom_bar(stat = "identity") +  
  facet_wrap(~source) + 
  theme_light()
```